### 2017-03-23 ThesisText/background.tex
Adds information on tools

The practical component of this project was developed entirely using Python and
some Python libraries which are relevant in. The version of CPython used was
version 3.5.2. The python libraries Pandas, version 0.19.2, was used for
statistical analysis, exploration, and preprocessing. The library SciKit-Learn,
version 0.18.1, was used to perform Data Mining tasks. SciKit-Learn uses Numpy
and Scikit, in versions 1.11.3 and 0.18.1 respectively. To output some graphs,
the python library Mat Plot Lib, version 1.5.4, was used.

\TODO{State the actual methods and algorithms in SciKit-Learn that were used}

>>>>

The practical component of this project was developed entirely using Python and
some Python libraries. The version of CPython used was version 3.5.2. The
python libraries Pandas, version 0.19.2, was used for statistical analysis,
exploration, and preprocessing. The library SciKit-Learn, version 0.18.1, was
used to perform Data Mining tasks. SciKit-Learn uses Numpy and Scikit, in
versions 1.11.3 and 0.18.1 respectively. To output some graphs, the python
library Mat Plot Lib, version 1.5.4, was used.

Decision trees and Bayesian Networks were used in this project. The algorithm
to train decision trees, implemented in the SciKit-Learn library, is an
optimized version of the CART algorithm~\cite{web_scikit_trees}. Bayesian
Networks are used in Naive Bayes tasks. The algorithm to train such models,
also implemented in SciKit-Learn, is Multinomial Naive
Bayes~\cite{web_scikit_bayes}.

Clustering is done using K-Means~\cite{web_scikit_kmeans} and Affinity
Propagation~\cite{web_scikit_affinity}. Both algorithms are implemented in
SciKit-Learn.
